Abstract Binding Trees

### 2015-10-25 paper.tex
wording/notation
Add parametric object-judgment
Add first paragraph of refinements section

\newcommand\IsAbt[5]{%
  \IMode{#1}\triangleright%
  \IMode{#2}\parallel%
  \IMode{#3}\vdash%
  \IMode{#4}:\OMode{#5}%
}

@@

This insight leads the way to a simple abt signature for the theory of telescopes
and sequents.
%
\newcommand\SortCtx{\mathsf{ctx}}
\newcommand\SortJdg{\mathsf{jdg}}
\newcommand\SortType{\mathsf{type}}
\newcommand\SortExpr{\mathsf{exp}}
\newcommand\OpNil{\mathsf{nil}}
\newcommand\OpSnoc[1]{\mathsf{snoc}[#1]}
\newcommand\OpVar[1]{\mathsf{var}[#1]}
\newcommand\OpSequent{\mathsf{sequent}}
%
\[
  \begin{array}{l}
    \IsSort{\SortCtx}\\
    \IsSort{\SortExpr}\\
    \IsSort{\SortType}\\
    \IsSort{\SortJdg}\\\\
    \IsOperator{\Upsilon, u:\SortExpr}{\OpVar{u}}{
      \MkArity{}{\SortExpr}
    }\\\\
    \IsOperator{\Upsilon}{\OpNil}{
      \MkArity{}{\SortCtx}
    }\\
    \IsOperator{\Upsilon, u:\SortExpr}{\OpSnoc{u}}{
      \MkArity{
        \MkValence{}{}{\SortCtx},
        \MkValence{}{}{\SortType}
      }{\SortCtx}
    }\\\\
    \IsOperator{\Upsilon}{\OpSequent}{
      \MkArity{
        \MkValence{}{}{\SortCtx},
        \MkValence{}{}{\SortType}
      }{\SortJdg}
    }
  \end{array}
\]

@@

%% TODO: add \nabla operator to close the context
%% TODO: implement refinement judgment for wellscopedness

>>>>

\newcommand\IsAbt[5]{%
  \IMode{#1}\triangleright%
  \IMode{#2}\parallel%
  \IMode{#3}\vdash%
  \IMode{#4}:\OMode{#5}%
}
\newcommand\IsWf[5]{%
  \IMode{#1}\triangleright%
  \IMode{#2}\parallel%
  \IMode{#3}\vdash%
  \IMode{#4}\in_{\mathbf{wf}}\OMode{#5}%
}

@@

This insight leads the way to a simple abt signature for the theory of telescopes
and sequents.
%
\newcommand\SortTele{\mathsf{tele}}
\newcommand\SortJdg{\mathsf{jdg}}
\newcommand\SortType{\mathsf{type}}
\newcommand\SortExpr{\mathsf{exp}}
\newcommand\OpNil{\mathsf{nil}}
\newcommand\OpSnoc[1]{\mathsf{snoc}[#1]}
\newcommand\OpVar[1]{\mathsf{var}[#1]}
\newcommand\OpSequent{\mathsf{sequent}}
%
\[
  \begin{array}{l}
    \IsSort{\SortTele}\\
    \IsSort{\SortExpr}\\
    \IsSort{\SortType}\\
    \IsSort{\SortJdg}\\\\
    \IsOperator{\Upsilon, u:\SortExpr}{\OpVar{u}}{
      \MkArity{}{\SortExpr}
    }\\\\
    \IsOperator{\Upsilon}{\OpNil}{
      \MkArity{}{\SortTele}
    }\\
    \IsOperator{\Upsilon, u:\SortExpr}{\OpSnoc{u}}{
      \MkArity{
        \MkValence{}{}{\SortTele},
        \MkValence{}{}{\SortType}
      }{\SortTele}
    }\\\\
    \IsOperator{\Upsilon}{\OpSequent}{
      \MkArity{
        \MkValence{}{}{\SortTele},
        \MkValence{}{}{\SortType}
      }{\SortJdg}
    }
  \end{array}
\]

@@

\newcommand\OpNabla[1]{\nabla[#1]}

The above sequent has free symbols, but we can close over them by adding a form
of parametric higher-order judgment to our object language, indexed by a
collection of sorts $\vec{s}$:
\[
  \IsOperator{\Upsilon}{\OpNabla{\vec{s}}}{
    \MkArity{
      \MkValence{\vec{s}}{}{\SortJdg}
    }{\SortJdg}
  }
\]

Then, we may write a closed sequent judgment as follows:
\[
  \IsAbt{\cdot}{\cdot}{\cdot}{
    \App{\OpNabla{\SortExp,\SortExp}}{
      \MkBTm{u,v}{}{
        \diamond,u:\OpBool,v:\App{\OpSo}{`u}%
        \gg%
        \App{\OpSo}{`u}
      }
    }
  }{\SortJdg}
\]

\subsection{Refinements for wellformedness}

Having specified an approximation of the grammar of telescopes and sequents in
the abt logical framework, we can proceed to define proper wellformedness via
\emph{inductive refinement}. The basic idea is to introduce a new form of
(meta)-judgment $\IsWf{\Omega}{\Upsilon}{\Gamma}{M}{s}$ which expresses the
extrinsic wellformedness properties we wish to verify, presupposing
$\IsAbt{\Omega}{\Upsilon}{\Gamma}{M}{s}$.

%% TODO: implement refinement judgment for wellscopedness
